Explanatory Data Analysis of Trade Statistics of Turkey

### 2018-12-22 Draft/Draft20181218.Rmd
.

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
subtitle: "MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group Fou\\*R* Term Project"
date: "December 2018"
output:
  html_document:
    toc: true
    #toc_float:
     # collapsed: true
      #smooth_scroll: true
    number_sections: false
    df_print: paged
    code_folding: hide
    theme: journal
    #highlight: tango

---

>>>>

---
title: "Explanatory Data Analysis of Trade Statistics of Turkey"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: true
    code_folding: hide
    df_print: paged
    number_sections: no
    theme: journal
    toc: yes
date: "December 2018"
subtitle: MEF University - BDA 503 Essentials of Data Analytics - Fall 2018 - Group
  Fou\*R* Term Project
---
